cardinalR: Generating interesting high-dimensional data structures

### 2025-10-07 paper-cardinalR.tex
Renumbered the sections

@@

\subsection{Usage}\label{usage}

\subsubsection{Main function}\label{main-function}

@@

\subsubsection{Shape generators}\label{shape-generators}

@@

\paragraph{Branching}\label{branching}

@@

\paragraph{Cone}\label{cone}

@@

\paragraph{Cube}\label{cube}

@@

\paragraph{Gaussian}\label{gaussian}

@@

\paragraph{Linear}\label{linear}

@@

\paragraph{Möbius}\label{muxf6bius}

@@

\paragraph{Polynomial}\label{polynomial}

@@

\paragraph{Pyramid}\label{pyramid}

@@

\paragraph{S-curve}\label{s-curve}

@@

\paragraph{Sphere}\label{sphere}

@@

\paragraph{Swiss Roll}\label{swiss-roll}

@@

\paragraph{Trefoil knots}\label{trefoil-knots}

@@

\paragraph{Trigonometric}\label{trigonometric}

@@

\subsubsection{Generate a spherical or hyperspherical hole within a structure}\label{generate-a-spherical-or-hyperspherical-hole-within-a-structure}

@@

\subsubsection{Generate noise dimensions}\label{generate-noise-dimensions}

@@

\subsubsection{Multiple cluster examples}\label{multiple-cluster-examples}

@@

\subsubsection{Additional functions}\label{additional-functions}

>>>>

\section{Usage}\label{usage}

@@

\subsection{Main function}\label{main-function}

@@

\subsection{Shape generators}\label{shape-generators}

@@

\subsubsection{Branching}\label{branching}

@@

\subsubsection{Cone}\label{cone}

@@

\subsubsection{Cube}\label{cube}

@@

\subsubsection{Gaussian}\label{gaussian}

@@

\subsubsection{Linear}\label{linear}

@@

\subsubsection{Möbius}\label{muxf6bius}

@@

\subsubsection{Polynomial}\label{polynomial}

@@

\subsubsection{Pyramid}\label{pyramid}

@@

\subsubsection{S-curve}\label{s-curve}

@@

\subsubsection{Sphere}\label{sphere}

@@

\subsubsection{Swiss Roll}\label{swiss-roll}

@@

\subsubsection{Trefoil knots}\label{trefoil-knots}

@@

\subsubsection{Trigonometric}\label{trigonometric}

@@

\subsection{Generate a spherical or hyperspherical hole within a structure}\label{generate-a-spherical-or-hyperspherical-hole-within-a-structure}

@@

\subsection{Generate noise dimensions}\label{generate-noise-dimensions}

@@

\subsection{Multiple cluster examples}\label{multiple-cluster-examples}

@@

\subsection{Additional functions}\label{additional-functions}
